Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Edit the description of heteroskedastic DGP
We want to keep the average \sigma^2 equal to 1.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
ensures that the average standard deviation in a neighborhood aroundt the cutoff
equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
satisfies
\[
  z(\gamma)
    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{\gamma}
    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
\]
for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
homoskedastic.\footnote{%
  The values $\bar h$ and $\bar b$ are taken as the average values over 500
  homoskedastic simulations of the bandwidths returned by CCT's optimal
  bandwidth selector. This ensures that the relevant variance around the cutoff
  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
This is the experimental design used by \citet{IK} and CCT for homoskedastic
simulations, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature.  The form of
heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
$gamma$ equal to 0 and 2 for the simulations.
We use the same three functional forms for $\mu_{j}$ as CCT.

>>>>

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
ensures that the average variance in a neighborhood around the cutoff
equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
satisfies
\[
  z(\gamma)^2
    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
\]
for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
homoskedastic.\footnote{%
  The values $\bar h$ and $\bar b$ are taken as the average values over 500
  homoskedastic simulations of the bandwidths returned by CCT's optimal
  bandwidth selector. This ensures that the relevant variance around the cutoff
  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
This is the experimental design used by \citet{IK} and CCT for homoskedastic
simulations, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature.  The form of
heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
$\gamma$ equal to 0 and 2 for the simulations.
We use the same three functional forms for $\mu_{j}$ as CCT.
